Discon analysis

### 2018-11-07 analysis/01_analysis.Rmd
mumble mumble experiment

files <- dir("../../adult_600_raw_data/sandbox-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_raw_data/sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

>>>>

files <- dir("../../adult_600_visual/sandbox-results/")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("../../adult_600_visual/sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}
